%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (adapted for user)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Edrian Miguel E. Capistrano} \\ \vspace{1pt}
    \small 0976-490-7611 $|$ \href{mailto:edrian.miguel.capistrano@student.ateneo.edu}{\underline{edrian.miguel.capistrano@student.ateneo.edu}} $|$ 
    \href{https://linkedin.com/in/yanicells}{\underline{linkedin.com/in/yanicells}} $|$
    \href{https://github.com/yanicells}{\underline{github.com/yanicells}} $|$
    \href{https://yanicells.dev}{\underline{yanicells.dev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ateneo de Manila University}{Expected Graduation: 2028}
      {Bachelor of Science in Computer Science, 2nd Year --- Cumulative QPI: 3.91}{Quezon City, PH}
    \resumeSubheading
      {La Salle Academy}{2018 -- 2024}
      {Junior High Valedictorian; Senior High Valedictorian (Highest Honor)}{Iligan City, PH}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IT Skills \& Development Officer, MISA (Management Information Systems Association)}{Aug 2025 -- Present}
      {Ateneo de Manila University}{Quezon City, PH}
      \resumeItemListStart
        \resumeItem{Designed and ran recurring technical workshops and onboarding sessions, increasing new member contribution rate to project repositories by improving tooling familiarity and documentation.}
        \resumeItem{Maintained and enhanced association websites and internal systems to support event registration and communications, reducing manual registration issues and support requests.}
        \resumeItem{Coordinated cross-team standardization of development tooling and onboarding docs to accelerate developer ramp-up for events and hackathons.}
      \resumeItemListEnd

    \resumeSubheading
      {Developer, Computer Society of the Ateneo}{Oct 2025 -- Present}
      {Ateneo de Manila University}{Quezon City, PH}
      \resumeItemListStart
        \resumeItem{Architected and implemented responsive web applications and websites for organizational events, delivering production-ready code with clear documentation and maintainable structure.}
        \resumeItem{Established code review and testing practices for student projects, improving release stability and reducing regressions during events.}
        \resumeItem{Collaborated with product and design stakeholders to translate requirements into implemented features and accessible UIs.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Developer, Google Developer Groups on Campus Loyola}{Sep 2025 -- Present}
      {Ateneo de Manila University}{Quezon City, PH}
      \resumeItemListStart
        \resumeItem{Built and maintained RESTful APIs and database schemas to securely expose application data to front-end clients and event dashboards.}
        \resumeItem{Defined API contracts and partnered with front-end engineers to optimize end-to-end performance and reliability during high-traffic events.}
        \resumeItem{Monitored service performance and tuned queries to improve response times under concurrent usage.}
      \resumeItemListEnd

    \resumeSubheading
      {Documentation Core Team (Photo \& Video), Geekshop — CompSAt}{Jul 2025 -- Present}
      {Computer Science Association (CompSAt)}{Ateneo de Manila University}
      \resumeItemListStart
        \resumeItem{Led visual documentation for events, producing photo and video assets used in promotions and archival records; improved asset retrieval times via organized storage conventions.}
      \resumeItemListEnd

    \resumeSubheading
      {Writing Assistant (ARISE), SOSE Newsletter}{2025 -- Present}
      {School of Science and Engineering, Ateneo de Manila University}{Quezon City, PH}
      \resumeItemListStart
        \resumeItem{Interviewed and drafted technical and community articles to increase newsletter engagement and accurately communicate research and student activities.}
      \resumeItemListEnd

    \resumeSubheading
      {STEM Strand Vice Governor, Supreme Student Government}{2023 -- 2024}
      {La Salle Academy}{Iligan City, PH}
      \resumeItemListStart
        \resumeItem{Directed planning and logistics for large student events (Sportsfest, La Salle Fair), coordinating teams and vendors to deliver events on schedule and within budgetary constraints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Redhead Redemption} $|$ \emph{Java, Sockets, Multithreading, OOP}}{Mar 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Built a LAN-based multiplayer top-down shooter with custom server/client networking and a multithreaded server to handle concurrent players and game state synchronization.}
            \resumeItem{Implemented enemy AI, item mechanics, and level design; optimized networking and game loop to maintain stable gameplay under concurrent connections.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CityCraft} $|$ \emph{Java, Swing, AWT, Audio Programming}}{Feb 2025 -- Mar 2025}
          \resumeItemListStart
            \resumeItem{Developed an animated 2D cityscape with dual-player controls, dynamic lighting, weather systems, and event-driven architecture for smooth animations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{NASA APIs Explorer} $|$ \emph{Node.js, Express, TailwindCSS, REST APIs}}{Aug 2025 -- Oct 2025}
          \resumeItemListStart
            \resumeItem{Created a full-stack app aggregating NASA APIs to present images, media, and Mars data with interactive visualizations and backend caching for faster browsing.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Musicells} $|$ \emph{React, Vite, TailwindCSS, Spotify API}}{Sep 2025 -- Oct 2025}
          \resumeItemListStart
            \resumeItem{Built a responsive React app for searching and favoriting albums using the Spotify API; handled OAuth flows and client-side state for user sessions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{UniSort} $|$ \emph{Node.js, Express, TailwindCSS, PostgreSQL}}{Sep 2025}
          \resumeItemListStart
            \resumeItem{Implemented a personality-quiz web app that recommends universities based on scoring logic, secure authentication, and persistent result storage.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Blogcells \& Travel-Tracker} $|$ \emph{Node.js, Express, PostgreSQL, TailwindCSS/Bootstrap}}{Aug 2025 -- Sep 2025}
          \resumeItemListStart
            \resumeItem{Built a blog platform (posts, comments, likes) and a country-tracking app with user profiles and CRUD features, focusing on clean UX and backend validation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, HTML/CSS, SQL} \\
     \textbf{Frameworks \& Libraries}{: React, Next.js, Node.js, Express, Django, Vite, TailwindCSS, Bootstrap, EJS, Zustand, Drizzle ORM} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, Vercel, JetBrains, VS Code, WSL, Docker, PostgreSQL, Neon} \\
     \textbf{Other}{: REST APIs, Authentication (OAuth), Testing, Multithreading, Socket Programming}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
